Syntactic realization with data-driven neural tree grammars

### 2016-10-10 paper/draft.tex
-some changes to related work

The grammar induction of \ref{sec:tree} allows us to construct an
inventory of supertags to match a corpus.  For NLG, we also need to
predict how likely a supertag is to fit a specific lexical item in the
context of a generation task.  We approach this problem using neural
networks. 
%
In particular, this work makes two contributions to improve stochastic
tree modeling with neural networks.
%
First, we represent supertags as vectors through embedding techniques
that enable to model to generalize naturally over complex, but related
structures.
%
Second, we address the hierarchical dependence between choices using a
recurrent tree network that can capture long-distance influences as
well as local ones.
%
We now describe these representations in more detail.

@@

For both stochastic tree models, a recurrent neural network language model is used to complete the linearization task.
%Both models produce partial results which a recurrent neural network language model is used to complete the linearization task.
%
%It is important to note that it is the same language model
%By using the same language model to finishing linearizing the output of both models, any observed differences in performance can be localized to the performance of the stochastic tree models.
%
The same language model is to eliminate the confound of
language model performance and measure performance differences in the
stochastic tree modeling.
%

@@

Using the representations of \ref{sec:neural}, the models of
\ref{sec:models} can be instantiated in six different ways.  We can
use a feed-forward Fergus-N architecture or a recurrent Fergus-R
architecture.  Each architecture can embed supertags \emph{minimally},
by learning a scalar corresponding to each supertag; \emph{atomically}, by learning an
embedding vector corresponding to each supertag; or
\emph{structurally}, by using convolutional coding over each
supertag's tree structure.

@@

Figure~\ref{table:linresults} shows the NLG evaluation results for the
different models.
%
The performance confirms our expectation that differences in supertag
accuracy after decoding correlate with NLG accuracy overall, but that
differences in NLG performance are attenuated.
%
We note by comparison that Bangalore and Rambow report an accuracy of
74.9\% in their best evaluation of FERGUS---on a data set of just 100
sentences with an average length of XXX.
%
Our evaluation, on XXX sentences with an average length of XXX, is much
more strenuous.

@@

There are several lines of related work which explore stochastic tree
models from the standpoint of parsing and understanding, including
networks that maintain state using recurrences and networks that
agglomerate information using tree traversals.
%
We think the perspective given by NLG is instructive.

Most similar to ours, is the top down tree structure of \newcite{zhang2016top}.
%
In this model, first, two long short-term memory (LSTM) networks are
used to make branch exploration decisions, and then an additional two
LSTM networks are used to continue along these branches.
%
The work of \newcite{Tai2015} similarly use an LSTM, but instead work
from the leaves upward to merge the hidden states of children inside
the recurrent step.
%
The upward merging of children to form representations for parents has
also been studied as pairwise agglomerations using recursive neural
networks \cite{Socher2010}.

A growing body of work investigates modeling long distance
relationships using efficient stacks in modern neural architecture.
%
\newcite{dyer2015transition} utilize an indexable LSTM as a neural
stack for transition-based parsing.
%
Similarly, \newcite{bowman2016fast} utilize both a stack and buffer
for sentence comprehension by utilizing an indexable structure and
performing computations with indices to these structures.
%
Finally, recent work models long distance relationships using the
dynamic composability in ApolloCaffe, a fork of the Caffe library
\cite{jia2014caffe}, to build different network structures based on
parse trees \cite{Andreas2016LearningTC}.

@@

>>>>

The grammar induction of \ref{sec:tree} allows us to construct an
inventory of supertags to match a corpus.  For NLG, we also need to
predict how likely a supertag is to fit a specific lexical item in the
context of a generation task.  We approach this problem using neural
networks. 
%
In particular, this work makes two contributions to improve stochastic
tree modeling with neural networks.
%
First, we represent supertags as vectors through embedding techniques
that enable to model to generalize over complex, but related
structures.
%
Second, we address the hierarchical dependence between choices using a
recurrent tree network that can capture long-distance influences as
well as local ones.
%
We now describe these representations in more detail.

@@

For both stochastic tree models, a recurrent neural network language model is used to complete the linearization task.
%Both models produce partial results which a recurrent neural network language model is used to complete the linearization task.
%
%It is important to note that it is the same language model
%By using the same language model to finishing linearizing the output of both models, any observed differences in performance can be localized to the performance of the stochastic tree models.
%
The same language model is used to eliminate the confound of
language model performance and measure performance differences in the
stochastic tree modeling.
%

@@

Using the representations of \ref{sec:neural}, the models of
\ref{sec:models} can be instantiated in six different ways.  We can
use a feed-forward Fergus-N architecture or a recurrent Fergus-R
architecture.  Each architecture can embed supertags \emph{minimally},
by learning a scalar corresponding to each supertag; \emph{atomically}, by learning an
embedding vector corresponding to each supertag; or
\emph{structurally}, by using convolutional coding over each
supertag's tree structure to form a vector.
%
In each case, the vector (a size-one vector in the \emph{mimimal} condition) is concatenated as described in \ref{sec:models}.

@@

Figure~\ref{table:linresults} shows the NLG evaluation results for the
different models.
%
The performance confirms our expectation that differences in supertag
accuracy after decoding correlate with NLG accuracy overall, but that
differences in NLG performance are attenuated.
%
We note by comparison that Bangalore and Rambow report an accuracy of
74.9\% in their best evaluation of FERGUS---on a data set of just 100
sentences with an average length of 16.7.
%
Our evaluation, on 2400 sentences with an average length of 22, is much
more strenuous.

@@

There are several lines of related work which explore stochastic tree
models from the standpoint of parsing and understanding.
%, including 
%networks that maintain state using recurrences and networks that
%agglomerate information using tree traversals.
%
We think the perspective given by NLG is instructive.
%
Where parsing infers most probable underlying structure, generation infers the most likely way of expressing a semantic structure---with which unlabeled dependency trees have served as our proxy in this work.

The works most similar to ours explicitly model tree structures, but focus on resolving the uncertainty invovled with the latent structure of an observed sentence. 
%
For example, the top down tree structure of \newcite{zhang2016top} expresses generation of a dependency structure as the decisions of a set of long short-term memory networks.  
%
The competing solutions are different tree structures which generate a single linear form.
%
In contrast, the generation problem is concerned with different linear forms that can result from the same tree structure.

Although the methodology presented in this work is closely related to several recent neural networks models for long-distance relationships, it differs distinctly in its treatment of state and search.
%
Specifically, forward-planning in a generation task produces a growing horizon of syntactic choices while shrinking the horizon of semantic goals.
%
At each step, a generator will choose amongst more possible syntactic operations with a limited number of goals in mind. 
%
In contrast, parsing and understanding begins with the surface form and constructs the organized semantic content, either for a downstream decision or for its own sake. 
%
The most notable works in this line of research are the recurrent neural network grammars \cite{dyer2016recurrent}, a shift-reduce parser and interpreter \cite{bowman2016fast}, and a dynamic network for composing other neural network modules \cite{Andreas2016LearningTC}. 
%
Interestingly, there is a common theme of using indexable data structures in neural architecture to make long-distance decisions.

@@

In generating the tree structure, it is optimized 
While this generates a tree structure, it is optimized to discover the most likely dependency structure that matches an input linear form.  
%
In this model, first, two long short-term memory (LSTM) networks are
used to make branch exploration decisions, and then an additional two
LSTM networks are used to continue along these branches.
%
The work of \newcite{Tai2015} similarly use an LSTM, but instead work
from the leaves upward to merge the hidden states of children inside
the recurrent step.
%
The upward merging of children to form representations for parents has
also been studied as pairwise agglomerations using recursive neural
networks \cite{Socher2010}.

differs in its emphasis on

A growing body of work investigates modeling long distance
relationships using efficient stacks in modern neural architecture.
%
\newcite{dyer2015transition} utilize an indexable LSTM as a neural
stack for transition-based parsing.
%
Similarly, \newcite{bowman2016fast} utilize both a stack and buffer
for sentence comprehension by utilizing an indexable structure and
performing computations with indices to these structures.
%
Finally, recent work models long distance relationships using the
dynamic composability in ApolloCaffe, a fork of the Caffe library
\cite{jia2014caffe}, to build different network structures based on
parse trees.
